\section{Questions}

\subsection{\Andy{I do not have any intuition about preservation ‘up to first order’.}}

\Henrik{%
Through a somewhat intransparent process (in the sense that I did not present their derivation in the \emph{Mathematica} notebook), I was able to determine the fundamental vector fields $\Funda[][\AmbSpace]$ for the three ``infinitesimal boosts'' $u$, $v$, $w \in \Lie(G)$, i.e. for three further generators that complement $\Lie(\SO(\AmbDim)) \oplus \Lie(\AmbSpace) \oplus \Lie(\R_{>0}) \subset \Lie(G)$, so that we obtain a full basis of $\Lie(G)$. 
In the notebook, I denoted these three fundamental vector fields by $U$, $V$, $W$, i.e., 
\begin{align*}
	U (x)
	\ceq K^{\AmbSpace}_u \at_x
	&=
	\begin{pmatrix}
		 x_1^2-x_2^2-x_3^2 \\
		 2 \, x_{1} \, x_{2} \\
		 2 \, x_{1} \, x_{3}
	\end{pmatrix}
	,
	\\
	V(x) \ceq K^{\AmbSpace}_v \at_x
		&=
	\begin{pmatrix}
		 2 \, x_2 \, x_1  \\
		 x_2^2-x_3^2-x_1^2 \\
		 2 \, x_2 \, x_3
	\end{pmatrix}
	,
	\\
	W(x) \ceq K^{\AmbSpace}_w\at_x
	&=
	\begin{pmatrix}
		2 \, x_3 \, x_1 \\
		2 \, x_3 \, x_2 \\
		x_3^2 -x_1^2 - x_2^2
	\end{pmatrix}
	.
\end{align*}
Thus by \eqref{eq:Funda}, we have 
\begin{align*}
	\Funda[u] \at_f =  U \circ f, 
	\quad
	\Funda[v] \at_f =  V \circ f, 
	\qand
	\Funda[w] \at_f =  W \circ f.
\end{align*}

We can now study area $\Area \colon \ConfSpace \to \R$ and enclosed volume $\Volume \colon \ConfSpace \to \R$ along an orbit $\Orbit \ceq (G f)$ of $G$. 
By the chain rule we have for each differentiable curve 
$g \colon ]-\epsilon,\epsilon[ \to G$ with $g(0) = 1$ and $g'(0) \in \Lie(G)$ 
that
\begin{align*}
		\frac{\dd}{\dd t} \Area( L_{g(t)}(f) ) \At_{t=0} = D \Area(f) \,(\Funda[\xi] \at_f)
\end{align*}
and analogously
\begin{align*}
		\frac{\dd}{\dd t} \Volume( L_{g(t)}(f) ) \At_{t=0} = D \Volume(f) \,(\Funda[\xi] \at_f).
\end{align*}

And what I did in the notebook is just checking for each torus $f$ of revolution with circular contour (TRCC for short) that
\begin{align}
	D \Area(f) \,(\Funda[u] \at_f) &= 0, \label{eq:DAU}
	\\
	D \Area(f) \,(\Funda[v] \at_f) &= 0, \label{eq:DAV}
	\\
	D \Area(f) \,(\Funda[w] \at_f) &= 0, \label{eq:DAW}
	\\
	D \Volume(f) \,(\Funda[u] \at_f) &= 0,  \label{eq:DVU}
	\\
	D \Volume(f) \,(\Funda[v] \at_f) &= 0,  \label{eq:DVV}
	\\
	D \Volume(f) \,(\Funda[w] \at_f) &= 0.  \label{eq:DVW}
\end{align}
I did so by parameterizing the torus by
\begin{align*}
	f( \varphi , \vartheta)
	\begin{pmatrix}
		\cos (\varphi ) (r \cos (\vartheta )+R)
		\\
		\sin (\varphi ) (r \cos (\vartheta )+R)
		\\
		r \,  \sin (\vartheta )
	\end{pmatrix}
	\quad
	\text{with some $R>0$ and some $r>0$.}
\end{align*}
We know that
\begin{align*}
	D\Area(f) \, X
	=
	\int_M \ninnerprod{H_f, X}\, \vol_f
	\qand
	D\Area(f) \, X
	=
	\int_M \ninnerprod{\nu_f, X}\, \vol_f	,
\end{align*}
where $H_f$ and $\nu_f$ are mean curvature vector and outward pointing normal of $f$.
Observe that
\begin{align*}
	\vol_f = r \, \sqrt{(R + r \cos(\vartheta))^2},
	\quad
	\nu_f = \tfrac{\partial}{\partial r} f(\varphi,\theta) = 
	\begin{pmatrix}
		\cos(\vartheta ) \, \cos (\varphi)
		\\
		\cos(\vartheta) \, \sin(\varphi)
		\\
		\sin(\vartheta)
	\end{pmatrix}
	\qand
	H_f(\varphi,\vartheta) = h(\theta) \, \nu_f
	,
\end{align*}
where $h(\theta)$ denotes the magnitude of the mean curvature vector which -- by rotation symmetry -- does not depend on the angle $\varphi$.
Thus, we can write down the \eqref{eq:DAU}--\eqref{eq:DVW} explicitly.
Then we just have to exploit symmetry properties of the trigonometric functions $\sin$ and $\cos$.

\bigskip

Of course, this does not necessarily imply that $\Area$ and $\Volume$ are constant on the whole orbit $\mathcal{O} = (G f)$, not even on an arbitrarily small neighborhood of $f$. 
While the boost $\exp(t \, w)$ ``in $z$-direction'' (along the axis of revolution) sends a TRCC to a TRCC (the contour has to be circular again and boosting along the axis of revolution preserves rotation symmetry; the parameterization might change considerably, but we are not interested in the parameterization, right?), the boosts $\exp(t \, u)$ and $\exp(t \, v )$ along the $x$ and $y$ direction should deform TRCC into Dupin cyclides. And so I do not expect that $\exp(t \,u)$, $\exp(t \,v)$ preserve both area and volume. But I could be wrong.
}%

\subsection{\Andy{With your symbolic setup in \emph{Mathematica} Henrik, is it easy to look at the 2nd order change? Maybe we will even see what makes the Clifford torus isoperimetric ratio so special?}}

\Henrik{%
Could be worth a try. Computing the Hessian at a critical point is typically not that difficult because it actually does not depend on the employed Riemannian metric and its connection:

Denote the orbit of $f$ under $G$ by $\Orbit = L_G(f)$. The fundamental vector fields $\Funda$ span the tangent space  $T_f  \Orbit$. If $\Function \colon \Orbit \to \R$ is twice differentiable, then for any Riemannian metric $h$ on $\Orbit$ we have
\begin{align*}
 	\Hess^{h}(\Function)( \Funda[\xi] , \Funda[\eta]) 
 	= 
 	\bigparen{ \Funda[\xi] \Funda[\eta] \Function } \at_f 
 	- 
 	\dd \Function(f) \, \nabla^h_{\Funda[\xi]} \Funda[\eta],
 	\quad
 	\text{for all $\xi$, $\eta \in \Lie(G)$,}
\end{align*} 	
where $\nabla^h$ is the Levi-Civita connection of $h$.
So in general, the result depends on the choice of a metric! But if $\dd \Function \at f = 0$ (like in the cases $\Function = \Area |_{\Orbit}$ and $\Function = \Volume |_{\Orbit}$ for example), then the metric-dependent term just vanishes and we get
\begin{align*}
 	\Hess^{h}(\Function)(f) ( \Funda[\xi] , \Funda[\eta]) 
 	= 
 	\bigparen{ \Funda[\xi] \Funda[\eta] \Function } \at_f 
	.
\end{align*}
And we (or rather \emph{Mathematica}) should be able to compute the latter, once we have figured out how the exponentials for the infinitesimal boost $u$, $v$, $w$ actually look like \ldots

\bigskip

Caution: If I am not mistaken, this does \emph{not} imply
\begin{align*}
	\bigparen{ \Funda[\xi] \Funda[\eta] \Area } \at_f 
	=
	D^2 \Area(f)( \Funda[\xi] , \Funda[\eta]),
\end{align*}
where $D^2$ denotes the second derivative on the surrounding Banach space!
This has to do with the fact that the orbit is a curved submanifold of $\ConfSpace$ and that $D\Area(f) \neq 0$. ( We only know that $D\Area(f)$ vanishes when multiplied against fundamental vector fields 
$\Funda[u]\at_f$, $\Funda[v]\at_f$, $\Funda[w]\at_f$ (and against any fundamental vector fields of the group of Euclidean motions, of course).
}%
